A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-16 results.tex
Caption changes

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/timeBetweenSxTx-unsat/timeBetweenSxTx-multiplot-unsat-TON.eps}
		\caption{Average time between successful transmissions in non-saturated conditions: averaging over all stations. \textcolor{red}{this figure needs new data files}}
		\label{fig:timeBetweenSxTx-multiplot-unsat}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/throughput-per-protocol/throughput-per-protocol-TON.eps}
		\caption{Average throughput per MAC protocol in a saturated mixed network}
		\label{fig:mixThroughput-sat-perProtocol-TON}
	\end{figure}

>>>>

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/timeBetweenSxTx-unsat/timeBetweenSxTx-multiplot-unsat-TON.eps}
		\caption{Average time between successful transmissions in non-saturated conditions: averaging over all stations}
		\label{fig:timeBetweenSxTx-multiplot-unsat}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/throughput-per-protocol/throughput-per-protocol-TON.eps}
		\caption{Average station throughput per MAC protocol in a saturated mixed network}
		\label{fig:mixThroughput-sat-perProtocol-TON}
	\end{figure}
